Luminance constancy under fixed geometry

### 2018-05-02 Draft4/draft4.tex
small edits

Recall that there are two qualitatively distinct aspects to the variation in light source spectra.
One is a variation in relative spectral power distribution and the
other is a variation in overall intensity.
To separate the effect of these two aspects, we trained and evaluated AMA on the contrast normalized cone isomerizations.
Figure~\ref{fig:Condition2}(c, d)shows that performance improves greatly, and indeed is essentially perfect.
This observation is consistent with a large literature on computational color constancy that shows that when only illumination spectra are varied,
contrast-based representations provide an effective vehicle for achieving color constancy (REFS).
That same literature, however, shows that
contrast-based representations are less effective at supporting constancy when the spectra of background objects in the scene vary.

@@

In Condition 3, we introduced variation in the reflectance spectra of the background objects.
This condition models the full real-world spectral variation that is most relevant for the computational problem of luminance constancy.
We again trained and evaluated AMA for labeled images patches in this condition using the contrast-normalized cone isomerizations.
Figure~\ref{fig:case3Estimates} shows the results.
The LRV estimates obtained via AMA are more variable and less accurate than for the previous conditions.
None-the-less, the estimates provide useful information about the target LRV.
Indeed, on average the estimates track the true LRV, as seen by the fact that the mean estimate
(red line) tracks the positive diagonal.
The increased estimation variability is indicated by the width of the shaded red region.
Performance of baseline linear regression method (also for the contrast normalized isomerizations) is worse than that of the AMA-based estimates.

>>>>

Recall that there are two qualitatively distinct aspects to the variation in light source spectra.
One is a variation in relative spectral power distribution and the
other is a variation in overall intensity.
To separate the effect of these two aspects, we trained and evaluated AMA on the contrast normalized cone isomerizations.
Figure~\ref{fig:Condition2}(c, d) shows that performance improves greatly, and indeed is essentially perfect.
This observation is consistent with a large literature on computational color constancy that shows that when only illumination spectra are varied,
contrast-based representations provide an effective vehicle for achieving color constancy (REFS).
That same literature, however, shows that
contrast-based representations are less effective at supporting constancy when the spectra of background objects in the scene vary.

@@

In Condition 3, we introduced variation in the reflectance spectra of the background objects.
This condition models the full real-world spectral variation that is most relevant for the computational problem of luminance constancy.
We again trained and evaluated AMA for labeled images patches in this condition using the contrast-normalized cone isomerizations 
(Figure~\ref{fig:case3Estimates}).
The LRV estimates obtained via AMA are more variable and less accurate than for the previous conditions.
None-the-less, the estimates provide useful information about the target LRV.
Indeed, on average the estimates track the true LRV, as seen by the fact that the mean estimate
(red line) tracks the positive diagonal.
The increased estimation variability is indicated by the width of the shaded red region.
Performance of baseline linear regression method (also for the contrast normalized isomerizations) is worse than that of the AMA-based estimates.
